Multi-channel Kondo model URG

### 2021-11-27 notes/multi-channel-urg.tex
compared thermal entropy with that of 1d ising

\section{Thermal entropy at \(T=0\)}
The thermal entropy at temperature \(T\) is given by
\begin{equation}\begin{aligned}
	S(T) = -k_B \sum_{n}P_n \ln P_n
\end{aligned}\end{equation}
where \(n\) sums over all eigenstates of the system. The state \(n\) is understood to have an energy \(E_n\). \(P_n\) is the probability to find the system in the state \(n\) from a canonical ensemble at temperature \(T\). This probability is given by
\begin{equation}\begin{aligned}
	P_n = \frac{e^{-\beta E_n}}{Z}
\end{aligned}\end{equation}
where \(Z = \sum_n d_n e^{-\beta E_n}\) and \(d_n\) is the degeneracy of the state \(E_n\). Substituting this gives for the entropy:
\begin{equation}\begin{aligned}
	S(T) = -k_B \sum_{n}\frac{e^{-\beta E_n}}{Z} \ln \frac{e^{-\beta E_n}}{Z}
\end{aligned}\end{equation}
Taking the limit of \(\beta \to \infty\) gives \(Z \to d_\text{gs}e^{-\beta E_\text{gs}}\):
\begin{equation}\begin{aligned}
	S(T) = -k_B \frac{d_\text{gs} e^{-\beta E_\text{gs}}}{d_\text{gs}e^{-\beta E_\text{gs}}} \ln \frac{e^{-\beta E_\text{gs}}}{d_\text{gs}e^{-\beta E_\text{gs}}} = k_B \ln d_\text{gs}
\end{aligned}\end{equation}
\begin{figure}[!ht]
	\centering
	\includegraphics[width=0.6\textwidth]{../numerics/entropy_comparison.pdf}
	\caption{Comparison of star graph zero temperature entropy with CFT/Bethe ansatz formula}
\end{figure}

\appendix
\clearpage
\section{URG analysis of the single-channel Kondo model}
\label{1KondoURG}
\begin{equation}\begin{aligned}
	\mathcal{H} = \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{k,l} J^z S_d^z s^z_{kl} + \frac{1}{2}\sum_{k,l} J^t \left(S_d^+ s^-_{kl}  + S_d^- s^+_{kl}\right)
\end{aligned}\end{equation}
where \(s^z_{kl} = \frac{1}{2}\left(c^\dagger_{k\uparrow}c_{l \uparrow} - c^\dagger_{k\downarrow}c_{l \downarrow}\right)\), \(s^-_{kl} = c^\dagger_{k \downarrow}c_{l \uparrow}\) and \(s^+_{kl} = {s^-_{lk}}^\dagger\). Also, \(\tau = \hat n - \frac{1}{2}\). \(k,l\) sum over the momentum states. \(\vec S_d\) is the impurity spin operator.

>>>>

\section{Thermal entropy at \(T=0\)}
Given the Helmholtz free energy \(F = -k_B T \ln Z = - \frac{1}{\beta} \ln\sum_n e^{-\beta E_n}\), the thermal entropy at temperature \(T\) is given by
\begin{equation}\begin{aligned}
	S(T) = - \frac{\partial{F}}{\partial{T}} = k_B \ln\sum_n e^{-\beta E_n} + \frac{\sum_n E_n e^{-\beta E_n}}{T \sum_n e^{-\beta E_n}}
\end{aligned}\end{equation}
In the limit of \(T \to 0\), only the lowest energy state \(E_\text{gs}\) will survive. Assuming this state has a degeneracy \(d_\text{gs}\), we have
\begin{equation}\begin{aligned}
	S(T \to 0) = k_B \ln\left(d_\text{gs} e^{-\beta E_\text{gs}}\right) + \frac{d_\text{gs} E_\text{gs}e^{-\beta E_\text{gs}}}{T d_\text{gs} e^{-\beta E_\text{gs}}} = k_B \ln d_\text{gs} - \frac{1}{T}E_\text{gs} + \frac{1}{T}E_\text{gs} = k_B \ln d_\text{gs}
\end{aligned}\end{equation}
This is a general result that holds for any system with a \(d_\text{gs}\)-fold degenerate ground state. For the star graph problem, we have a \(K-\)fold degenerate ground state, so the \(T=0\) entropy of the star graph Hamiltonian with \(K\) outer spins is
\begin{equation}\begin{aligned}
	S(T\to 0) = k_B \ln K
\end{aligned}\end{equation}

\begin{figure}[!ht]
	\centering
	\includegraphics[width=0.5\textwidth]{../numerics/entropy_comparison.pdf}
	\caption{Comparison of star graph zero temperature entropy with CFT/Bethe ansatz formula}
\end{figure}

Another related problem for which this result holds is the Ising model on a 1D chain. The partition function for that problem is \(Z = \lambda_1^N + \lambda_2^N\), where \(\lambda_{1,2} = e^{\beta J} \pm e^{-\beta J} \) are the eigenvalues of the \(T-\)matrix and \(N\) is the number of particles. As we come to \(T \to 0\), we have \(\lambda_{1,2} \simeq e^{\beta J}\) and \(Z \simeq 2 e^{\beta N J}\), so \(F = -k_B T \ln 2 - N J\) and the entropy becomes \(S = - \partial_T F = k_B \ln 2\). Note that the factor of 2 in \(Z\) is the degeneracy \(d_\text{gs}\) described above.

\clearpage
\appendix
\section{URG analysis of the single-channel Kondo model}
\label{1KondoURG}
\begin{equation}\begin{aligned}
	\mathcal{H} = \sum_{k\sigma}\epsilon_{k}\tau_{k\sigma} + \sum_{k,l} J^z S_d^z s^z_{kl} + \frac{1}{2}\sum_{k,l} J^t \left(S_d^+ s^-_{kl}  + S_d^- s^+_{kl}\right)
\end{aligned}\end{equation}
where \(s^z_{kl} = \frac{1}{2}\left(c^\dagger_{k\uparrow}c_{l \uparrow} - c^\dagger_{k\downarrow}c_{l \downarrow}\right)\), \(s^-_{kl} = c^\dagger_{k \downarrow}c_{l \uparrow}\) and \(s^+_{kl} = {s^-_{lk}}^\dagger\). Also, \(\tau = \hat n - \frac{1}{2}\). \(k,l\) sum over the momentum states. \(\vec S_d\) is the impurity spin operator.
